---
title: "Introduction to medicode"
author: "Chi Zhang"
date: "2023-02-27"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to medicode}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

`medicode` is a utility tool that contains metadata for medical classification and clinical coding. 

The motivation is two-fold: 

* Standardization: in Norway, some systems (such as hospital electronic health record systems) have only **Norwegian coding and abbreviations**, which can be inconvenient to read for human researchers, and standardize in reports.
* Reference: `medicode` provides a consistent way to extract corresponding code range, such as a list of **causes of death**. 

## List of code for Cause of death

```{r echo=TRUE}
code_death <- medicode::cause_of_death
head(code_death)
```


## ICD-10 code

The English version ([source](https://www.cms.gov/medicare/coordination-benefits-recovery-overview/icd-code-lists))

```{r echo=TRUE}
head(medicode::icd10_en)
```

The Norwegian version ([source](https://www.ehelse.no/kodeverk-terminologi/kodeverket-icd-10-og-icd-11))

```{r echo=TRUE}
head(medicode::icd10_no)
```



